# My First Knitr Document
Dr. Cocos

## Introduction

This is some text (i.e. a "text chunk")

Here is a code chunk (echo = FALSE) it will not be displayed in the final doc
```{r simulation, echo=FALSE}
set.seed(1)
x <- rnorm(100)
mean(x)
```

## in line Text Computations

```{r computetime, echo=TRUE}
time <- format(Sys.time(),"%a %b %d %X %Y")
rand <- rnorm(1)
```

The current time is `r time` and my favorite randome number is `r rand`

## Incorporating graphics

```{r simulatedata,echo=TRUE}
x <- rnorm(100); y <- x + rnorm(100,sd=0.5)
```
Here is a scatterplot of the data
```{r scatterplot, fig.height=4}
par(mar=c(5,4,1,1),las=1)
plot(x,y,main = "My simulated data")
```

## Making tables with xtable

```{r fitmodel}
library(datasets)
data("airquality")
fit <- lm(Ozone ~ Wind + Solar.R + Temp, data = airquality)
```
Here is a table of regression coefficients
```{r showtable,results='asis'}
library(xtable)
xt <- xtable(summary(fit))
print(xt, type = "html")
```

## Setting global options

This setting will automatically set all code chunks to echo= FALSE
```{r setoptions,echo=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, results = "hide")
```

Nice to remember  
Output:  
- results = "asis" or "hide"  
- echo = TRUE, FALSE  
Figures  
- fig.height = numeric  
- fig.width = numeric  

For very large computations we can use the uption cache = TRUE, this way the output will be 
store in the disk and we do not need to re-run it.





